Models of VOR learning in MHC knockout mice

### 2013-02-13 Notes/VORmodel.tex
typos etc

We are also assuming that the relation between VOR gain and mean synaptic weight is the same for mutant ant wild-type, except for a linear offset to compensate for the difference in equlibrium weights mentioned above.

@@

This compound synapse would seem to have $2^P$ internal states.
However, we need only keep track of the number of potentiated synapses, not their identity, leaving $M=P+1$ states.
The transition network topology will then have a multistate toplogy (see \autoref{fig:models}\ref{fig:multistate_model}) but the transition probabilities will no longer be uniform and the weight of the compound synapse is the mean of its constituent synapses:
%
\begin{equation}\label{eq:pooledweight}
  \w_i = \frac{2i}{P}-1.
\end{equation}
%

@@

\resultsfig{multistate_med}{Simulation results for the multistate model with intermediate training ($\Delta f=-0.17$)}

>>>>

We are also assuming that the relation between VOR gain and mean synaptic weight is the same for mutant ant wild-type, except for a linear offset to compensate for the difference in equilibrium weights mentioned above.

@@

This compound synapse would seem to have $2^P$ internal states.
However, we need only keep track of the number of potentiated synapses, not their identity, leaving $M=P+1$ states.
The transition network topology will then have a multistate topology (see \autoref{fig:models}\ref{fig:multistate_model}) but the transition probabilities will no longer be uniform and the weight of the compound synapse is the mean of its constituent synapses:
%
\begin{equation}\label{eq:pooledweight}
  \w_i = \frac{2i}{P}-1.
\end{equation}
%

@@

\resultsfig{multistate_med}{Simulation results for the multistate model with moderate training ($\Delta f=-0.17$)}
